---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(FSA)
```

# Load in data 
```{r}
survey <- read.csv("C:\\Users\\lmlev\\iCloudDrive\\UMN\\Bayer Fellowship\\FinalDataFile_Survey_results.csv")
```

# Knowledge Comparisons 
## Add knowledge level to survey data 
```{r}
# assign knowledge level for Q13
for (i in 1:nrow(survey)){
  if ((str_detect(survey$Q13[i], "Phosphorus"))){
    survey$kq13[i] <- as.numeric(1)
  } else {
    survey$kq13[i] <- as.numeric(0)
  }
}

# Assign knowledge Value for question Q15
for (i in 1:nrow(survey)){
  if ((str_detect(survey$Q15[i], "Algae blooms"))){
    survey$kq15[i] <- as.numeric(1)}
  else {
    survey$kq15[i] <- as.numeric(0)}
}

# Knowledge for participants split into three levels: 0, 1, and 2 
survey$know <- as.numeric((survey$kq13 + survey$kq15))
survey$knowledge <- survey$know #Factor version of the knowledge level 

# Create classes 0 to 5 for previous knowledge 
survey$knowledge[survey$knowledge == 0] <- "no knowledge"
survey$knowledge[survey$knowledge == 1] <- "some knowledge"
survey$knowledge[survey$knowledge == 2] <- "knowledgeable"

survey$knowledge <- as.factor(survey$knowledge)
```

## General Knowledge (Q13 and Q15) vs Actual Knowledge Ranking (q14)
```{r}
# Question 13 Knowledge
q13 <- survey %>% 
  drop_na(Q14_1) %>%
  group_by(Q14_1 , Q13) %>%
  summarize(count = n())
q13

ggplot(q13, aes(Q14_1, count, fill = Q13)) + geom_bar(stat = 'identity', position = "dodge")

q15 <- survey %>%
  drop_na(Q14_1) %>%
  group_by(Q14_1, kq15) %>%
  summarize(count = n())
q15

ggplot(q15, aes(as.factor(Q14_1), count, fill = as.factor(kq15))) + geom_bar(stat = 'identity', position = "dodge")

# FINAL SUMMARY of knowledge level in comparison to claimed knowledge level 
know_sum <- survey %>%
  drop_na(Q14_1) %>%
  group_by(Q14_1, knowledge) %>%
  summarise(count = n())
know_sum


dunnTest(Q14_1~knowledge, survey) 
kruskal.test(Q14_1~knowledge, survey)
# Significant both ways, but not a useful insight 

# How many participants had previous knowledge (ACTUAL)
# (0) 139, (1) 149, (2) 276 
act_know <- survey %>%
  drop_na(Q14_1) %>%
  group_by(knowledge) %>%
  summarize(total = n())
act_know

# How did participants rank their knowledge level
# (0) 142, (1) 173, (2) 111, (3) 91, (4) 34, (5) 13 
partic_know <- survey %>% 
  drop_na(Q14_1) %>%
  group_by(Q14_1) %>%
  summarize(total = n())
partic_know

know_sum
# Many people who ranked their knowledge as zero were actually able to answer at least one of the questions correctly (88 out of 139)
# Of those that ranked themselves as highly knowledgeable (13), 4 got at least one question incorrect (30% of respondents)
# In general people were unable to correctly classify their own knowledge. 

# Kruskal Wallis test cannot have an ordered factor 
know_sum$knowledge <- factor(know_sum$knowledge, ordered = TRUE, 
                                levels = c("no knowledge", 
                                           "some knowledge", 
                                           "knowledgeable"))

# FIGURE FOR PAPER 
ggplot(know_sum, aes(as.factor(Q14_1), count, fill = knowledge)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Knowledge Rank by Participant", 
       fill = "Actual Knowledge\nLevel", 
       y = "Responses") +
  scale_fill_manual(values = c("#F8766D", "#00BA38", "#619CFF"))

```

## Is knowledge difference between rural, suburban and urban populations.
### No, there is no significant differences between the rural and suburban populations (not with urban)
```{r}
# Is ACTUAL knowledge level influenced by rural, urban, suburban background?
kruskal.test(know~Q8, data = survey)

#perform Dunn's Test with Bonferroni correction for p-values
dunnTest(know ~ Q8,
         data=survey,
         method="bonferroni")

# Plot for knowledge by rural/urban
ggplot(survey, aes(knowledge, fill = Q8)) + geom_bar(position = "dodge")


# Participant Ranking of Knowledge 
# Is knowledge ranking influenced by rural, urban, suburban background?
kruskal.test(Q14_1~Q8, data = survey)

#perform Dunn's Test with Bonferroni correction for p-values
dunnTest(Q14_1 ~ Q8,
         data=survey,
         method="bonferroni")

# FIGURE FOR PAPER
ggplot(data=subset(survey, !is.na(Q14_1)), aes(as.factor(Q14_1), fill = Q8)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(x = "Self Identified Knowledge Level (Selected by Participant)", 
       y = "Number of Participants") +
  scale_fill_hue("")
# Rural populations were believed they had more knowledge than those from Urban and Suburban populations

```

## Knowledge Comparison - Farmers vs everyone else
### No significant difference in knowledge between farmers and everyone else 
```{r}
``{r}
# assign Farmer status 
for (i in 1:nrow(survey)){
  if (survey$Q20[i] == c("Producer/Farmer")){
    survey$Farmer[i] <- as.character("Yes")}
  else {
    survey$Farmer[i] <- as.character("No")
  }
}

survey$Farmer <- as.factor(survey$Farmer)

farmers <- survey %>%
  group_by(Farmer) %>%
  summarize(count = n())
farmers

# Farmer Summary 
qknow <- survey %>%
  group_by(know, Farmer) %>%
  summarize(count = n(), 
            perc_farmer = (count/30)*100, 
            perc_nofarmer = (count/567)*100)
qknow

# Is Age statistically different between Farmers and not Farmers? 
farmer_sum <- survey %>%
  group_by(Q2, Farmer) %>%
  summarise(count = n())
farmer_sum

ggplot(farmer_sum, aes(Q2, count, fill = Farmer)) + geom_bar(stat = "identity", fun.y = "mean", position = "dodge")

kruskal.test(Q2~Farmer, survey)
# Age is not a significantly affected by if the respondent is a farmer. 

library(dplyr)
detach(package:plyr, unload=TRUE)

farmer_sum2 <- survey %>%
  group_by(knowledge, Farmer) %>%
  summarise(count = n(), 
            perc_farm = (count/30)*100, 
            perc_nonfarm = (count/567)*100)
farmer_sum2
# 30 farmers and 567 others 
# Not a farmer Knowledge ranking: 0 knowledge: 26%, 1: 50%, 2:24% 
# Farmer Knowledge: 0 knowledge: 53%, 1: 23%, 2: 23%
# There is a significant difference in knowledge based on Farm background 

dunnTest(know ~ Farmer,
         data=survey,
         method="bonferroni")
kruskal.test(know~Farmer, survey)
# Dunn test reveals there IS a significant difference between farmers and non farmers. Farmers were MORE likely to be LESS knowledgeable. 

# Why did farmers get it wrong?
farmer_sum3 <- survey %>%
  group_by(Q13, Farmer) %>%
  summarise(count = n(), 
            perc_farm = (count/30)*100, 
            perc_nonfarm = (count/567)*100)
farmer_sum3

ggplot(farmer_sum3, aes(Q13, count, fill = Farmer)) + geom_bar(stat = "identity", position = "dodge")
# 40% of the time, Farmers thought N was the major contributor to algae blooms, where only 23% of respondents identified P correctly. For non farmers, there was no clear consensus. 22% bacteria, 25% N, and 26% P (the remainder was pesticides and synthetic chemicals)
# While farmers did get it wrong more often, they often selected the other major pollutant, Nitrogen. 63.3% identified the top two pollutants for water (P and N), but failed to identify which affects freshwater sources. Where as the general public selected the two top pollutants (N and P) only half of the time (51%). 

```



# Knowledge Comparison by industry, are members of the ag industry more knowledgeable? 
## No, statistical difference between industry knowledge and consumer knowledge 
```{r}
# assign knowledge level for Q17
for (i in 1:nrow(survey)){
  if (survey$Q20[i] == c("Consumer")){
    survey$Background[i] <- as.character("NoAg")}
  else {
    survey$Background[i] <- as.character("Ag")
  }
}

survey$Background <- as.factor(survey$Background)

back <- survey %>%
  group_by(Background) %>%
  summarise(count = n())
back
# 114 other, 483 just consumers 

backgroundsum <- survey %>%
  group_by(knowledge, Background) %>%
  summarise(count = n(), 
            perc_ag = (count/114)*100, 
            perc_noag = (count/483)*100)
backgroundsum
# Ag Knowledge ranking: 0 knowledge: 31%, 1: 42%, 2: 27%
# No Ag Knowledge ranking: 0 knowledge: 27% Ag, 1: 50%, 2: 23%

q13 <- survey %>%
  drop_na(Q13) %>%
  group_by(kq13, Background) %>%
  summarize(count = n(), 
            perc_ag = (count/114)*100, 
            perc_noag = (count/483)*100)
q13
# 68% of those with an ag background got q13 wrong. 75% of those without an ag background got q13 wrong 

q15 <- survey %>%
  drop_na(Q15) %>%
  group_by(kq15, Background) %>%
  summarize(count = n(), 
            perc_ag = (count/114)*100, 
            perc_noag = (count/483)*100)
q15
# 65% of those with an ag background were able to identify algae blooms. 71% of those without an ag background were also able to identify algae blooms 


# Knowledge by association
ggplot(survey, aes(Background, fill = knowledge)) + geom_bar(position = "dodge")

kruskal.test(knowledge~Background, survey)
# There is NO significant difference between the ag industry and consumers as far as knowledge 


# Subset the datasets to run the wilcoxon test 
ag_back <- subset(survey, Background == c("Ag"), na.action = "omit")
no_ag_back <- subset(survey, Background == c("NoAg"), na.action = "omit")


wilcox.test(no_ag_back$know, ag_back$know)
# Leads to the same p-value as the krusal walis analysis and Dunn's test 

mean(no_ag_back$know)
mean(ag_back$know)


backgroundsum2 <- survey %>%
  drop_na(Q14_1) %>%
  group_by(Q14_1, Background) %>%
  summarise(count = n(), 
            perc_ag = (count/111)*100, 
            perc_noag = (count/453)*100)
backgroundsum2

kruskal.test(Q14_1~Background, survey)
wilcox.test(no_ag_back$Q14_1, ag_back$Q14_1)

# FIGURE FOR PAPER
ggplot(subset(survey, !is.na(Q14_1)), aes(Background, fill = as.factor(Q14_1))) + geom_bar(position = "dodge") +
  scale_fill_hue("Self Assigned\nKnowledge Ranking") +
  labs(x = "Agricultural Affiliation", 
       y = "Number of Respondents") +
  scale_x_discrete(labels=c("Ag" = "Affiliated", "NoAg" = "No Affiliation"))


```

## Knowledge comparison by age
```{r}
age_know <- survey %>%
  group_by(Q2) %>%
  summarise(count = n())
age_know

age_know <- survey %>%
  group_by(Q2, knowledge) %>%
  summarise(count = n())
age_know

# FIGURE FOR PAPER 
ggplot(survey, aes(Q2, fill = knowledge)) + 
  geom_bar(position = "dodge") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_hue("Actual Knowledge")+ 
  labs(x = "Age", 
       y = "Number of Respondents")
  

age_know2 <- survey %>%
  group_by(Q2) %>%
  summarise(count = n(), 
            mean = mean(know))
age_know2

# FIGURE FOR PAPER
ggplot(age_know2, aes(Q2, mean, fill = Q2)) + 
  geom_bar(position = "dodge", stat = "identity") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_hue("")+ 
  labs(x = "", 
       y = "Average Knowledge Level")

kruskal.test(know~Q2, survey)
dunnTest(know~Q2, survey)

```


# Attitude towards water quality
## Algae Bloom Concern
### Concern was not different between ag and no ag backgrounds NOR urban v rural v suburban populations 
```{r}
# Concern towards algae blooms 
survey$Q12 <- as.numeric(survey$Q12)

attit <- survey %>%
  group_by(Q12, Background) %>%
  summarise(mean = mean(Q12),
            count = n())
attit

ggplot(attit, aes(Q12, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

ggplot(ag_back, aes(Q12)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q12)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("No Knowledge Response for 9.1")

ggplot(no_ag_back, aes(Q12)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q12)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("No Knowledge Response for 9.1")


wilcox.test(ag_back$Q12, no_ag_back$Q12)

survey$q12 <- as.numeric(survey$Q12)
kruskal.test(Q12 ~ Q8, survey)

```

# Concern about water quality across all groups 
```{r}
concern <- survey %>%
  group_by(Q9_3) %>%
  summarise(count = n())
concern
```

# Concern about water quality in Minnesota by ag vs no ag background 
```{r}
# Concern about water quality for ag vs no ag background 
ggplot(survey, aes(Background, Q9_1, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")
ggplot(survey, aes(Background, Q9_2, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")
ggplot(survey, aes(Background, Q9_3, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")

ggplot(survey, aes(Q9_3)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q9_3)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("")

mean(survey$Q9_1)
mean(survey$Q9_2)
mean(survey$Q9_3)


# Concern about drinking and hygiene 
wilcox.test(ag_back$Q9_1, no_ag_back$Q9_1)

# This is significantly different suburban vs urban concern 
drink <- survey %>%
  group_by(Q9_1, Background) %>%
  summarise(mean = mean(Q9_1),
            count = n())
drink 

ggplot(drink, aes(Q9_1, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_1 ~ Q8, survey)
dunnTest(Q9_1 ~ Q8, survey)

# Concern about recreation 
wilcox.test(ag_back$Q9_2, no_ag_back$Q9_2)
# This is significantly difference 
rec <- survey %>%
  group_by(Q9_2, Background) %>%
  summarise(mean = mean(Q9_2),
            count = n())
rec

ggplot(rec, aes(Q9_2, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_2 ~ Q8, survey)

# Concern about environment 
wilcox.test(ag_back$Q9_3, no_ag_back$Q9_3)
# This is also significantly different between the two groups 
envir <- survey %>%
  group_by(Q9_3, Background) %>%
  summarise(mean = mean(Q9_3),
            count = n())
envir

ggplot(envir, aes(Q9_3, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_3 ~ Q8, survey)

```


# Concern about water quality in Minnesota by age 
```{r}
age <- survey %>%
  group_by(Q2) %>%
  summarize(count = n())
age

age_concern <- survey %>%
  group_by(Q2, Q9_3) %>%
  summarize(count = n(),
            perc_18 = (count/127)*100,
            perc_25 = (count/105)*100, 
            perc_35 = (count/74)*100, 
            perc_45 = (count/108)*100, 
            perc_55 = (count/117)*100, 
            perc_65 = (count/56)*100, 
            perc_75 = (count/10)*100
  )
age_concern


ggplot(age, aes(Q9_3, count, fill = Q2)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

# How did respondents grade their knowledge by age 
age <- survey %>%
  drop_na (Q14_1) %>% 
  group_by(Q2) %>%
  summarize(count = n())
age


age_know <- survey %>%
  drop_na(Q14_1)
  group_by(Q2, Q14_1) %>%
  summarize(count = n(),
            perc_18 = (count/118)*100,
            perc_25 = (count/98)*100, 
            perc_35 = (count/71)*100, 
            perc_45 = (count/104)*100, 
            perc_55 = (count/111)*100, 
            perc_65 = (count/53)*100, 
            perc_75 = (count/9)*100
  )
age_know

ggplot(age_know, aes(Q14_1, count, fill = Q2)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")



```


# Source of information
```{r}
info_source <- survey %>% 
  drop_na(Q19) %>%
  group_by(Q19 ) %>%
  summarize(count = n(), 
            perc = (count/595)*100)
info_source

total = sum(info_source$count)
# 595 answers for the new sources 

# Overview 
info_source <- survey %>% 
  drop_na(Q19) %>%
  group_by(Q8 , Q19 ) %>%
  summarize(count = n())
info_source


info <- spread(info_source, Q8, count)

ggplot(info_source, aes(Q19, count, fill = Q8)) + geom_bar(stat = 'identity', position = "dodge")

kruskal.test(Q19 ~ Q8, survey)

# Rural 
rural_N <- count(survey, Q8 == "Rural")[2, 2]

news_rural <- survey %>%
  subset(Q8 == "Rural") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/rural_N*100)
news_rural

#Suburban
suburban_N <- count(survey, Q8 == "Suburban")[2, 2]

news_suburban <- survey %>%
  subset(Q8 == "Suburban") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/suburban_N*100)
news_suburban

#Urban 

urban_N <- count(survey, Q8 == "Urban")[2, 2]

news_urban <- survey %>%
  subset(Q8 == "Urban") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/urban_N*100)
news_urban



# News based on age

infoage <- survey %>% 
  drop_na(Q19) %>%
  group_by(Q2) %>%
  summarize(count = n())
infoage
# Remove one value from the 18 and 25 age groups (2 nas)

info_age <- survey %>% 
  drop_na(Q19) %>%
  group_by(Q2 , Q19 ) %>%
  summarize(count = n(),
            perc_18 = (count/126)*100,
            perc_25 = (count/104)*100, 
            perc_35 = (count/74)*100, 
            perc_45 = (count/108)*100, 
            perc_55 = (count/117)*100, 
            perc_65 = (count/56)*100, 
            perc_75 = (count/10)*100)
info_age


# create bar plot
pie = ggplot(info_age, aes(x = Q19, y = count, fill = Q19)) +
  geom_bar(stat = "identity", position = "dodge", width = 1) +
  facet_wrap(~ Q2)

pie
             
ggplot(info_age, aes(Q19, count, fill = Q2)) + geom_bar(stat = 'identity', position = "dodge")

kruskal.test(Q19 ~ Q2, survey)
dunnTest(Q19~Q2, survey)
```


# What is the major cause of P water pollution? Q17 
```{r}

pollution <- survey %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/594)*100)
pollution  

pollution_ag <- ag_back %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/114)*100)
pollution_ag  

count(no_ag_back)
pollution_noag <- no_ag_back %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/483)*100)
pollution_noag  

```

# Q13 
```{r}

chem <- survey %>% 
  group_by(Q13) %>%
  summarise(count = n(), 
            perc = (count/594)*100)
chem  

chem_ag <- ag_back %>% 
  group_by(Q13) %>%
  summarise(count = n(), 
            perc = (count/114)*100)
chem_ag  

count(no_ag_back)
chem_noag <- no_ag_back %>% 
  group_by(Q13) %>%
  summarise(count = n(), 
            perc = (count/483)*100)
chem_noag  

```


Q16
```{r}
q16 <- read.csv("C:/Users/lmlev/iCloudDrive/UMN/Bayer Fellowship/Q16_Survey.csv")

ggplot(q16 , aes(x= Q16_0_GROUP, color = Q8, fill = Q8)) +
  geom_bar() +
   #scale_color_manual(values=c('dodgerblue2'))+
   #ylab("Percent RTLDG") +
   #xlab("Percent Change in UAV Height") +
   theme(plot.title = element_text(hjust = 0.5, size = 15),
          # axis.text=element_text(size=13, colour = "black"),
          # axis.title=element_text(size=14),
          axis.text.x = element_text(angle = 45))
          # legend.text = element_text(size=14, colour = "black")) 

# Highest Contributors
ggplot(q16 , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

# Highest Contibutor
ggplot(q16 , aes(x= Q16_0_GROUP, color = Q8, fill = Q8)) +
  geom_bar() 
+
  theme(axis.text.x = element_text(angle = 45))

k1 <- kruskal.test(Q16_HIGH1 ~ Q8, data = q16)


kruskal.test(Q16_HIGH1 ~ Q8, data = q16)


Rural<-subset(q16, Q8=='Rural',na.action = "omit") 
#Rural n = 106
  
Suburban<-subset(q16, Q8=='Suburban',na.action = "omit") 
#Suburban n = 298

Urban<-subset(q16, Q8=='Urban',na.action = "omit")
# Urban n = 193

ggplot(Rural , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))



ggplot(Urban , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))



ggplot(Suburban , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

# Highest Contributor 

ggplot(Rural , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

ggplot(Urban , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

ggplot(Suburban , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))


summarize(Rural, 
          )


kruskal.test(Q12~Q8.1, data = SurveyDataMO)



```

# CODE ARCHIVE 
## Question 17 analysis before question was dropped 
```{r}

## assign knowledge level for Q17
# for (i in 1:nrow(survey)){
#   if ((str_detect(survey$Q17[i], "Erosion"))){
#     survey$kq17[i] <- as.numeric(2)}
#   else if ((str_detect(survey$Q17[i], "Cropland runoff"))){
#       survey$kq17[i] <- as.numeric(2)}
#   else if ((str_detect(survey$Q17[i], "Application of fertilizers"))){
#       survey$kq17[i] <- as.numeric(1)}
#   else {
#     survey$kq17[i] <- as.numeric(0)}
# }

# # Question 17 Knowledge
# q17 <- survey %>% 
#   drop_na(Q14_1) %>%
#   group_by(Q14_1 , Q17 ) %>%
#   summarize(count = n())
# q17
# 
# ggplot(q17, aes(Q14_1, count, fill = Q17)) + geom_bar(stat = 'identity', position = "dodge")
# 
# # Question 13 and 17 summary
# # Summary of knowledge including the knowledge questions and also the participants ranking of their own knowledge 
# q13_17 <- survey %>% 
#   drop_na(Q14_1) %>%
#   group_by(Q14_1 , Q17 , Q13) %>%
#   summarize(count = n())
# q13_17
# 
```



## Q15 function for multiple points for knowledge 
```{r}
# Function for assigning a knowledge value for Q15
q15 <- function(survey){
  
  # Assign knowledge Value for question Q15 for the algae blooms
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Algae blooms"))){
      survey$kq15_1[i] <- as.numeric(1)}
    else {
      survey$kq15_1[i] <- as.numeric(0)}
  }
  
  
  # Loops for the correct values for the lesser point question values 
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Death of fish and other aquatic life"))){
      survey$k1[i] <- as.numeric(.25)}
    else {
      survey$k1[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Eutrophication"))){
      survey$k2[i] <- as.numeric(.25)}
    else {
      survey$k2[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Toxic drinking water"))){
      survey$k3[i] <- as.numeric(.25)}
    else {
      survey$k3[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Skin rashes with contact"))){
      survey$k4[i] <- as.numeric(.25)}
    else {
      survey$k4[i] <- as.numeric(0)}
  }
  
  # For loops for the incorrect answers 
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Flooding"))){
      survey$k5[i] <- as.numeric(-.25)}
    else {
      survey$k5[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Waterborne pathogens"))){
      survey$k6[i] <- as.numeric(-.25)}
    else {
      survey$k6[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Disease from consumption"))){
      survey$k7[i] <- as.numeric(-.25)}
    else {
      survey$k7[i] <- as.numeric(0)}
  }
  
  for (i in 1:nrow(survey)){
    if ((str_detect(survey$Q15[i], "Heavy Metal Contamination"))){
      survey$k8[i] <- as.numeric(-.25)}
    else {
      survey$k8[i] <- as.numeric(0)}
  }

  survey$kq15 <- as.numeric(survey$kq15_1 + survey$k1 + survey$k2 + survey$k3 + survey$k4 + survey$k5 + survey$k6 + survey$k7 + survey$k8)
  survey <- select(survey, -c("k1":"k8", "kq15_1"))
  return(survey)
}
survey <- q15(survey)

```



## Old knowledge levels, using 3 categories 
```{r Old knowledge levels (3 categories)}
# survey$knowledge <- as.numeric((survey$kq13 + survey$kq15 + survey$kq17)/2)
# 
# survey$know[survey$know <= 1] <- "No previous knowledge"
# survey$know[survey$know <= 2.5 & survey$know > 1] <- "Some knowledge"
# survey$know[survey$know <= 3 & survey$know > 2.5] <- "Previous knowledge"

# # How many participants with previous knowledge 
# # 35 with knowledge, 201 with some knowledge, and 328 with no knowledge 
# know5 <- know3 %>% 
#   group_by(knowledge) %>%
#   summarize(total = sum(count))
# know5


# # Graphing the knowledge levels 
# know4$Q14_1 <- as.factor(know4$Q14_1)
# know4$knowledge <- as.factor(know4$knowledge)
# 
# library(plyr)
# library(plyr)
# know4$knowledge <- mapvalues(know4$knowledge, from = c(0,1, 2), to = c("No Previous Knowledge", "Some Previous Knowledge", "Previous Knowledge"))
# 
# 
# # FIGURE 1. Knowledge comparison among participants 
# ggplot(know4, aes(Q14_1, total, fill = k_no)) + 
#   geom_bar(stat = "identity", position = "dodge") +
#   labs(x = "Knowledge Rank by Participant", 
#        fill = "Actual Knowledge Level", 
#        y = "Responses") 
```


## Label knowledge level in the survey data 
```{r}
# Create empty columns to assign knowledge level (high, mod, low)
survey$know1 <- NA
survey$know2 <- NA

# assign knowledge level for Q13
for (i in 1:nrow(survey)){
  if ((str_detect(survey$Q13[i], "Phosphorus"))){
    survey$know1[i] <- as.numeric(1)
  } else {
    survey$know1[i] <- as.numeric(0)
  }
}

survey$know2 <- as.numeric(0)

# assign knowledge level for Q17
for (i in 1:nrow(survey)){
  if (str_detect(survey$Q17[i], "Erosion|Cropland runoff")){
    survey$know2[i] <- as.numeric(1)}
  else {
    survey$know2[i] <- as.numeric(0)
  }
}

# Knowledge for participants split into three levels: 0, 1, and 2 
survey$knowledge <- as.numeric(survey$know1 + survey$know2)
survey$know <- as.factor(survey$knowledge)


low_know <- survey %>%
  filter(knowledge == 0) %>%
  summarise(count = n())
low_know
# 351 with no knowledge, 59% 


```
