---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(FSA)
```

# Load in data 
```{r}
survey <- read.csv("C:/Users/lmlev/iCloudDrive/UMN/Bayer Fellowship/FinalDataFile_Survey_R.csv")
```

# Source of information
```{r}

# Overview 
info_source <- survey %>% 
  drop_na(Q19) %>%
  group_by(Q8 , Q19 ) %>%
  summarize(count = n())
info_source



info <- spread(info_source, Q8, count)

ggplot(info_source, aes(Q19, count, fill = Q8)) + geom_bar(stat = 'identity', position = "dodge")

# Rural 
rural_N <- count(survey, Q8 == "Rural")[2, 2]

news_rural <- survey %>%
  subset(Q8 == "Rural") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/rural_N*100)
news_rural

#Suburban
suburban_N <- count(survey, Q8 == "Suburban")[2, 2]

news_suburban <- survey %>%
  subset(Q8 == "Suburban") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/suburban_N*100)
news_suburban

#Urban 

urban_N <- count(survey, Q8 == "Urban")[2, 2]

news_urban <- survey %>%
  subset(Q8 == "Urban") %>%
  group_by(Q19) %>%
  summarise(n = n(), 
            perc = n/urban_N*100)
news_urban


```

# General Knowledge vs Actual Knowledge Ranking
```{r}
# Question 13 Knowledge
know <- survey %>% 
  drop_na(Q14_1) %>%
  group_by(Q14_1 , Q13 ) %>%
  summarize(count = n())
know

ggplot(know, aes(Q14_1, count, fill = Q13)) + geom_bar(stat = 'identity', position = "dodge")

# Question 17 Knowledge
know2 <- survey %>% 
  drop_na(Q14_1) %>%
  group_by(Q14_1 , Q17 ) %>%
  summarize(count = n())
know2

ggplot(know2, aes(Q14_1, count, fill = Q17)) + geom_bar(stat = 'identity', position = "dodge")

# Question 13 and 17 summary
# Summary of knowledge including the knowledge questions and also the participants ranking of their own knowledge 
know3 <- survey %>% 
  drop_na(Q14_1) %>%
  group_by(Q14_1 , Q17 , Q13) %>%
  summarize(count = n())
know3

# Create empty columns to assign knowledge level (high, mod, low)
know3$know1 <- NA
know3$know2 <- NA

# assign knowledge level for Q13
for (i in 1:nrow(know3)){
  if ((str_detect(know3$Q13[i], "Phosphorus"))){
    know3$know1[i] <- as.numeric(1)
  } else {
    know3$know1[i] <- as.numeric(0)
  }
}

# assign knowledge level for Q17
for (i in 1:nrow(know3)){
  if ((str_detect(know3$Q17[i], "Erosion"))){
    know3$know2[i] <- as.numeric(1)}
  else if ((str_detect(know3$Q17[i], "Cropland runoff"))){
      know3$know2[i] <- as.numeric(1)}
  else {
    know3$know2[i] <- as.numeric(0)}
}

# Knowledge for participants split into three levels: 0, 1, and 2 
know3$knowledge <- as.numeric(know3$know1 + know3$know2)


# FINAL SUMMARY of knowledge level in comparison to claimed knowledge level 
know4 <- know3 %>% 
  group_by(Q14_1 , knowledge) %>%
  summarize(total = sum(count))
know4

# How many participants with previous knowledge 
# 35 with knowledge, 201 with some knowledge, and 328 with no knowledge 
know5 <- know3 %>% 
  group_by(knowledge) %>%
  summarize(total = sum(count))
know5

# How did participants rank their knowledge level (0-1) (2-3) (4-5)
# 47 high knowledge, 202 with moderate knowledge, 315 little knowledge 
know6 <- know3 %>% 
  group_by(Q14_1) %>%
  summarize(total = sum(count))
know6


# Graphing the knowledge levels 
know4$Q14_1 <- as.factor(know4$Q14_1)
know4$knowledge <- as.factor(know4$knowledge)

library(plyr)
library(plyr)
know4$knowledge <- mapvalues(know4$knowledge, from = c(0,1, 2), to = c("No Previous Knowledge", "Some Previous Knowledge", "Previous Knowledge"))


# FIGURE 1. Knowledge comparison among participants 
ggplot(know4, aes(Q14_1, total, fill = knowledge)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Knowledge Rank by Participant", 
       fill = "Actual Knowledge Level", 
       y = "Responses") 

# Run next block before these 
# kruskal.test(Q14_1~knowledge, survey)
# dunnTest(Q14_1~knowledge, survey)


```

# Label knowledge level in the survey data 
```{r}
# Create empty columns to assign knowledge level (high, mod, low)
survey$know1 <- NA
survey$know2 <- NA

# assign knowledge level for Q13
for (i in 1:nrow(survey)){
  if ((str_detect(survey$Q13[i], "Phosphorus"))){
    survey$know1[i] <- as.numeric(1)
  } else {
    survey$know1[i] <- as.numeric(0)
  }
}

survey$know2 <- as.numeric(0)

# assign knowledge level for Q17
for (i in 1:nrow(survey)){
  if (str_detect(survey$Q17[i], "Erosion|Cropland runoff")){
    survey$know2[i] <- as.numeric(1)}
  else {
    survey$know2[i] <- as.numeric(0)
  }
}

# Knowledge for participants split into three levels: 0, 1, and 2 
survey$knowledge <- as.numeric(survey$know1 + survey$know2)
survey$know <- as.factor(survey$knowledge)


low_know <- survey %>%
  filter(knowledge == 0) %>%
  summarise(count = n())
low_know
# 351 with no knowledge, 59% 


```

# Is knowledge difference between rural, suburban and urban populations.
## Yes, there is significant differences between the rural and suburban populations (not with urban)
```{r}
# Is knowledge level influenced by rural, urban, suburban background?
kruskal.test(knowledge~Q8, data = survey)

#perform Dunn's Test with Bonferroni correction for p-values
dunnTest(knowledge ~ Q8,
         data=survey,
         method="bonferroni")


# Plot for knowledge by rural/urban
ggplot(survey, aes(know, fill = Q8)) + geom_bar(position = "dodge")
# Plot shows that across urban, suburban and urban poplutions the most common knowledge class was 0, followed by 1 then 2. Same pattern for all.
```

# Knowledge Comparison by industry, are members of the ag industry more knowledgeable? 
## Yes, statistical difference between industry knowledge and consumer knowledge 
```{r}
# assign knowledge level for Q17
for (i in 1:nrow(survey)){
  if (survey$Q20[i] == c("Consumer")){
    survey$Background[i] <- as.character("NoAg")}
  else {
    survey$Background[i] <- as.character("Ag")
  }
}

count(survey$Q20 == c("Consumer"))
# 114 other, 483 just consumers 

library(dplyr)
detach(package:plyr, unload=TRUE)

backgroundsum <- survey %>%
  group_by(knowledge, Background) %>%
  summarise(count = n())
backgroundsum
# Ag Knowledge ranking: 0 knowledge: 49% Ag, 1: 40%, 2:11% 
# No Ag Knowledge: 0 knowledge: 61%, 1: 34%, 2: 5%
# Ag background did translate to greater knowledge, test with non parametric test 

# Knowledge by association
ggplot(survey, aes(knowledge, fill = Background)) + geom_bar(position = "dodge")

# library(ggpubr)
# ggboxplot(survey, y = knowledge, x = Background)

# survey$Background <- as.factor(survey$Background)
# kruskal.test(knowledge~Background, survey)
# There is a significant difference between the ag industry and consumers as far as knowledge 

# dunnTest(knowledge ~ Background,
         # data=survey,
         # method="bonferroni")
# Dunn test reveals there is a significant difference in knowledge based on the industy vs not


# Subset the datasets to run the wilcoxon test 
ag_back <- subset(survey, Background == c("Ag"), na.action = "omit")
no_ag_back <- subset(survey, Background == c("NoAg"), na.action = "omit")

wilcox.test(no_ag_back$knowledge, ag_back$knowledge)
# Leads to the same p-value as the krusal walis analysis and Dunn's test 

mean(no_ag_back$knowledge)
mean(ag_back$knowledge)


ggplot(survey, aes(Background, knowledge, fill = knowledge)) + geom_bar(stat = "summary")

survey %>% 
  filter(Background == c("Ag")) %>%
  summarise(mean = mean(knowledge))

survey %>% 
  filter(Background == c("NoAg")) %>%
  summarise(mean = mean(knowledge))

```

# Knowledge Comparison - Farmers vs everyone else
## No significant difference in knowledge between farmers and everyone else 
```{r}
``{r}

# assign knowledge level for Q17
for (i in 1:nrow(survey)){
  if (survey$Q20[i] == c("Producer/Farmer")){
    survey$Farmer[i] <- as.character("Yes")}
  else {
    survey$Farmer[i] <- as.character("No")
  }
}

library(dplyr)
detach(package:plyr, unload=TRUE)

farmer_sum <- survey %>%
  group_by(knowledge, Farmer) %>%
  summarise(count = n())
farmer_sum
# 30 farmers and 567 others 
# Not a farmer Knowledge ranking: 0 knowledge: 59% Ag, 1: 35%, 2:6% 
# Farmer Knowledge: 0 knowledge: 57%, 1: 33%, 2: 10%
# There is not a significant difference in knowledge based on Farm background 

dunnTest(knowledge ~ Background,
         data=survey,
         method="bonferroni")
# Dunn test reveals there is not a significant difference in knowledge based on farm background

```

# Attitude towards water quality
```{r}
# Concern towards algae blooms 
survey$Q12 <- as.numeric(survey$Q12)

attit <- survey %>%
  group_by(Q12, Background) %>%
  summarise(mean = mean(Q12),
            count = n())
attit

ggplot(attit, aes(Q12, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

ggplot(ag_back, aes(Q12)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q12)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("No Knowledge Response for 9.1")

ggplot(no_ag_back, aes(Q12)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q12)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("No Knowledge Response for 9.1")


wilcox.test(ag_back$Q12, no_ag_back$Q12)

survey$q12 <- as.numeric(survey$Q12)
kruskal.test(q12 ~ Background, survey)

```

# Concern about water quality across all groups 
```{r}
concern <- survey %>%
  group_by(Q9_3) %>%
  summarise(count = n())
concern
```

# Concern about water quality in Minnesota by ag vs no ag background 
```{r}
# Concern about water quality for ag vs no ag background 
ggplot(survey, aes(Background, Q9_1, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")
ggplot(survey, aes(Background, Q9_2, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")
ggplot(survey, aes(Background, Q9_3, fill = Background)) + geom_bar(stat = "summary", fun.y = "mean")

ggplot(survey, aes(Q9_3)) + geom_histogram(binwidth=1, color="black", fill="white")+geom_vline(aes(xintercept=mean(Q9_3)), color="blue", linetype="dashed", size=1)+labs(x="Level", y="Response Count") +ggtitle("")

mean(survey$Q9_1)
mean(survey$Q9_2)
mean(survey$Q9_3)


# Concern about drinking and hygiene 
wilcox.test(ag_back$Q9_1, no_ag_back$Q9_1)

# This is significantly different 
drink <- survey %>%
  group_by(Q9_1, Background) %>%
  summarise(mean = mean(Q9_1),
            count = n())
drink 

ggplot(drink, aes(Q9_1, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_1 ~ Q8, survey)
dunnTest(Q9_1 ~ Q8, survey)

# Concern about recreation 
wilcox.test(ag_back$Q9_2, no_ag_back$Q9_2)
# This is significantly difference 
rec <- survey %>%
  group_by(Q9_2, Background) %>%
  summarise(mean = mean(Q9_2),
            count = n())
rec

ggplot(rec, aes(Q9_2, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_2 ~ Q8, survey)

# Concern about environment 
wilcox.test(ag_back$Q9_3, no_ag_back$Q9_3)
# This is also significantly different between the two groups 
envir <- survey %>%
  group_by(Q9_3, Background) %>%
  summarise(mean = mean(Q9_3),
            count = n())
envir

ggplot(envir, aes(Q9_3, count, fill = Background)) + geom_bar(position = "dodge", stat = "summary", fun.y = "mean")

kruskal.test(Q9_3 ~ Q8, survey)

```


# What is the major cause of P water pollution? Q17 
```{r}

pollution <- survey %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/594)*100)
pollution  

pollution_ag <- ag_back %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/114)*100)
pollution_ag  

count(no_ag_back)
pollution_noag <- no_ag_back %>% 
  group_by(Q17) %>%
  summarise(count = n(), 
            perc = (count/483)*100)
pollution_noag  

```



Q16
```{r}
q16 <- read.csv("C:/Users/lmlev/iCloudDrive/UMN/Bayer Fellowship/Q16_Survey.csv")

ggplot(q16 , aes(x= Q16_0_GROUP, color = Q8, fill = Q8)) +
  geom_bar() +
   #scale_color_manual(values=c('dodgerblue2'))+
   #ylab("Percent RTLDG") +
   #xlab("Percent Change in UAV Height") +
   theme(plot.title = element_text(hjust = 0.5, size = 15),
          # axis.text=element_text(size=13, colour = "black"),
          # axis.title=element_text(size=14),
          axis.text.x = element_text(angle = 45))
          # legend.text = element_text(size=14, colour = "black")) 

# Highest Contributors
ggplot(q16 , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

# Highest Contibutor
ggplot(q16 , aes(x= Q16_0_GROUP, color = Q8, fill = Q8)) +
  geom_bar() 
+
  theme(axis.text.x = element_text(angle = 45))

k1 <- kruskal.test(Q16_HIGH1 ~ Q8, data = q16)


kruskal.test(Q16_HIGH1 ~ Q8, data = q16)


Rural<-subset(q16, Q8=='Rural',na.action = "omit") 
#Rural n = 106
  
Suburban<-subset(q16, Q8=='Suburban',na.action = "omit") 
#Suburban n = 298

Urban<-subset(q16, Q8=='Urban',na.action = "omit")
# Urban n = 193

ggplot(Rural , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))



ggplot(Urban , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))



ggplot(Suburban , aes(x= Q16_0_GROUP)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

# Highest Contributor 

ggplot(Rural , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

ggplot(Urban , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))

ggplot(Suburban , aes(x= Q16_HIGH1)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45))


summarize(Rural, 
          )


kruskal.test(Q12~Q8.1, data = SurveyDataMO)



```

